RationalGRL: A Framework for Argumentation and Goal Modeling

### 2018-05-02 Response to reviewers.txt

Reviewer 1 argues that the algorithms are fairly simple. We agree that many algorithms are very much the same, and we have therefore shortened the sections containing these algorithms: sections 5.4.1 to 5.4.3 now all contain one example of the specific type of algorithm instead of two. Reviewer 2 asks whether the automated reasoning can be handled by propositional logic instead of the algorithms. The answer is that propositional logic in itself does not contain specific algorithms for, for example, INTRO, REPLACE and DISABLE. Furthermore, the algorithms also introduce arguments and attacks, formal notions of which are not in basic propositional logic. The idea is that the formalization is needed for the algorithms, but that just providing a formal semantics of GRL does not directly tell you how to compute/reason with GRL models.

%FB: **Marc, can you work on shortening sections 5.4.1-5.4.3?**

-----------------------
%R1: The methodology and the tools looks quite preliminary and without a real validation of the approach. I think this is the weakest part of the paper. Authors should demonstrate the applicability, scalability and usefulness of their approach in the real word. The tool and the modeling language should be used and evaluated by practitioners while they cope with real requirements engineering problems and complexity issues.
%R2: I think that the relatively simple argument structures are appealing in the sense that the overhead for practical application may be tolerable. However, this remains to be shown yet in an industrial environment. Connecting them with an existing approach for goal modeling is also a pro in this respect.

%FB: Depending on the editor's answer we can leave this as is in the paper. However, we do need to come up withy a satisfactory example in the response to reviewers. Also, I think we need to include some references on empirical work that has been done on goal modelling

I asked Fabiano and he gave me the following two references, we can discuss them.

Estrada, H., Rebollar, A. M., Pastor, O., & Mylopoulos, J. (2006, June). An empirical evaluation of the i* framework in a model-based software generation environment. In International Conference on Advanced Information Systems Engineering (pp. 513-527). Springer, Berlin, Heidelberg.

Morandini, M., Marchetto, A., & Perini, A. (2011, August). Requirements comprehension: A controlled experiment on conceptual modeling methods. In Empirical Requirements Engineering (EmpiRE), 2011 First International Workshop on (pp. 53-60). IEEE

***Sepideh***

### 2018-05-02 Response to reviewers.txt

===== REPLY #2
We agree that many algorithms are very much the same, and we have therefore shortened the sections containing these algorithms: sections 5.4.1 to 5.4.3 now all contain one example of the specific type of algorithm instead of two or more.

===== COMMENT #3
The methodology and the tools looks quite preliminary and without a real validation of the approach. I think this is the weakest part of the paper. Authors should demonstrate the applicability, scalability and usefulness of their approach in the real word. The tool and the modeling language should be used and evaluated by practitioners while they cope with real requirements engineering problems and complexity issues.

===== REPLY #3
TODO: WRITE WHEN ANALYSIS IS DONE

%FB: Marc to write on Enterprise Architects

%FB: Marc/Floris to write on the below
I think we need to include some references on empirical work that has been done on goal modelling. I asked Fabiano and he gave me the following two references, we can discuss them.

Estrada, H., Rebollar, A. M., Pastor, O., & Mylopoulos, J. (2006, June). An empirical evaluation of the i* framework in a model-based software generation environment. In International Conference on Advanced Information Systems Engineering (pp. 513-527). Springer, Berlin, Heidelberg.

Morandini, M., Marchetto, A., & Perini, A. (2011, August). Requirements comprehension: A controlled experiment on conceptual modeling methods. In Empirical Requirements Engineering (EmpiRE), 2011 First International Workshop on (pp. 53-60). IEEE

### 2018-05-02 SUBMITTED_FILES/REJ_Submission_MarcvanZee_RationalGRL/designprompt.tex

\subsubsection*{Requirements}
The following broad requirements should be followed when designing this system:
\begin{enumerate}
\item
Students must be able to create a visual map of an area, laying out roads in a pattern of their choosing. The resulting map need not be complex, but should allow for roads of varying length to be placed, and different arrangements of intersections to be created. Your approach should readily accommodate at least six intersections, if not more.
\item
Students must be able to describe the behavior of the traffic lights at each of the intersections. It is up to you to determine what the exact interaction will be, but a variety of sequences and timing schemes should be allowed. Your approach should also be able to accommodate left-hand turns protected by left-hand green arrow lights. In addition:
\begin{enumerate}
\item
Combinations of individual signals that would result in crashes should not be allowed.
\item
Every intersection on the map must have traffic lights (there are not any stop signs, over- passes, or other variations). All intersections will be 4-way: there are no ``T'' intersections, nor one-way roads.
\item
Students must be able to design each intersection with or without the option to have sensors that detect whether any cars are present in a given lane. The intersection's lights' behavior should be able to change based on the input from these sensors, though the exact behavior of this feature is up to you.
\end{enumerate}
\item
Based on the map created, and the intersection timing schemes, the students must be able to simulate traffic flows on the map. The traffic levels should be conveyed visually to the user in a real-time manner, as they emerge in the simulation. The current state of the intersections' traffic lights should also be depicted visually, and updated when they change. It is up to you how to present this information to the students using your program. For example, you may choose to depict individual cars, or to use a more abstract representation.
\item
Students should be able to change the traffic density that enters the map on a given road. For ex- ample, it should be possible to create a busy road, or a seldom used one, and any variation in between. How exactly this is declared by the user and depicted by the system is up to you. Broadly, the tool should be easy to use, and should encourage students to explore multiple alternative approaches. Stu- dents should be able to observe any problems with their map's timing scheme, alter it, and see the results of their changes on the traffic patterns. This program is not meant to be an exact, scientific simulation, but aims to simply illustrate the basic effect that traffic signal timing has on traffic. If you wish, you may assume that you will be able to reuse an existing software package that provides relevant mathematical functionality such as statistical distributions, random number generators, and queuing theory.
\end{enumerate}

@@

Your design will primarily be evaluated based on its elegance and clarity – both in its overall solution and envisioned implementation structure.

\subsubsection*{Desired Outcomes}

Your work on this design should focus on two main issues:

\begin{enumerate}
\item
You must design the interaction that the students will have with the system. You should design the basic appearance of the program, as well as the means by which the user creates a map, sets traffic timing schemes, and views traffic simulations.
\item
You must design the basic structure of the code that will be used to implement this system. You should focus on the important design decisions that form the foundation of the implementation, and work those out to the depth you believe is needed.
\end{enumerate}

The result of this session should be: \emph{the ability to present your design to a team of software developers who will be tasked with actually implementing it.} The level of competency you can expect is that of students who just completed a basic computer science or software engineering undergraduate degree. You do not need to create a complete, final diagram to be handed off to an implementation team. But you should have an understanding that is sufficient to explain how to implement the system to competent developers, without requiring them to make many high-level design decisions on their own.

To simulate this hand-off, you will be asked to briefly explain the above two aspects of your design after the design session is over.

\subsubsection*{Timeline}
\begin{itemize}
\item 1 hour and 50 minutes: Design session
\item 10 minutes: Break / collect thoughts
\item 10 minutes: Explanation of your design 
\item 10 minutes: Exit questionnaire
\end{itemize}

>>>>

\subsubsection*{Requirements}
The following broad requirements should be followed when designing this system:
\begin{enumerate}
\item
Students must be able to create a visual map of an area, laying out roads in a pattern of their choosing. The resulting map need not be complex, but should allow for roads of varying length to be placed, and different arrangements of intersections to be created. Your approach should readily accommodate at least six intersections, if not more.
\item
Students must be able to describe the behavior of the traffic lights at each of the intersections. It is up to you to determine what the exact interaction will be, but a variety of sequences and timing schemes should be allowed. Your approach should also be able to accommodate left-hand turns protected by left-hand green arrow lights. In addition:
\begin{enumerate}
\item
Combinations of individual signals that would result in crashes should not be allowed.
\item
Every intersection on the map must have traffic lights (there are not any stop signs, over- passes, or other variations). All intersections will be 4-way: there are no ``T'' intersections, nor one-way roads.
\item
Students must be able to design each intersection with or without the option to have sensors that detect whether any cars are present in a given lane. The intersection's lights' behavior should be able to change based on the input from these sensors, though the exact behavior of this feature is up to you.
\end{enumerate}
\item
Based on the map created, and the intersection timing schemes, the students must be able to simulate traffic flows on the map. The traffic levels should be conveyed visually to the user in a real-time manner, as they emerge in the simulation. The current state of the intersections' traffic lights should also be depicted visually, and updated when they change. It is up to you how to present this information to the students using your program. For example, you may choose to depict individual cars, or to use a more abstract representation.
\item
Students should be able to change the traffic density that enters the map on a given road. For ex- ample, it should be possible to create a busy road, or a seldom used one, and any variation in between. How exactly this is declared by the user and depicted by the system is up to you. Broadly, the tool should be easy to use, and should encourage students to explore multiple alternative approaches. Students should be able to observe any problems with their map's timing scheme, alter it, and see the results of their changes on the traffic patterns. This program is not meant to be an exact, scientific simulation, but aims to simply illustrate the basic effect that traffic signal timing has on traffic. If you wish, you may assume that you will be able to reuse an existing software package that provides relevant mathematical functionality such as statistical distributions, random number generators, and queuing theory.
\end{enumerate}

@@

%I deleted the Desired Outcomes and Timeline, as the requirements are most important for our story.

### 2018-05-02 SUBMITTED_FILES/REJ_Submission_MarcvanZee_RationalGRL/examples.tex

We now discuss various instantiations of argument schemes and the result of answering critical questions in more detail. For each example, we provide transcript excerpts, a visualization of arguments, and the corresponding goal model elements. Figure~\ref{fig:transcripts:grl} in the previous section shows an example of how a RationalGRL may look like when it is developed in our prototype tool. However, the argument schemes that are instantiated are left implicit in this figure (in the tool, they can be seen in the details pane, see Section~\ref{sect:tool}). Since we would like to make these instantiated argument schemes explicit in the examples below, we use a different visual language here. We provide a legend for our visualization notation in Figure~\ref{fig:legend}.

>>>>

In the previous section we discussed the results of our empirical analysis, and we used a simplified version of one of the transcripts as a motivating example. In this section, we provide examples from all of the three transcripts in more detail. Note that the examples in this section do not always come from Figure~\ref{fig:transcripts:grl}, but they may come from any of the three transcripts.

For each example, we provide transcript excerpts, a visualization of arguments, and the corresponding goal model elements. As we explained in the previous section, Figure~\ref{fig:transcripts:grl} shows an example of how a RationalGRL model may look like when it is developed in our prototype tool. However, the argument schemes that are instantiated are left implicit in this figure (in the tool, they can be seen in the details pane, see Section~\ref{sect:tool}). Since we would like to make these instantiated argument schemes explicit in the examples below, we use a different visual language here. We provide a legend for our visualization notation in Figure~\ref{fig:legend}.
